Developing a preprint culture in biology

### 2012-10-02 ms.tex
add references

Furthermore, the review process as a whole is critically over-loaded, because
as the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
(REF), and when not invited to submit a revision, authors must start the whole
process all over again.  Initiatives to reduce time from submission to
publication have emerged across the scientific community. XXX et coll.  (TREE
paper recylce, reuse, ...) called for the recycling and reuse of peer-reviews:
by attaching previous reviews and detailed replies to a new submission, both
the editor and the referees can gauge the work done on the manuscript, and
perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
of Science} initiative allows authors to seek anonymous pre-review by their
peers. Some journals now accept to publish papers which received good
evaluations, with \emph{Animal Biology} having recently accepted first a paper
reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
outsourcing the review process. A widespread use of preprint servers can
achieve the same goal of reducing the time spent in review. By putting a
manuscript for open comments and criticisms, the authors will receive valuable
feedback and can improve the version which will be submitted. With a rich
enough community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread and will overall
increase the quality of first submissions.

>>>>

Furthermore, the review process as a whole is critically over-loaded, because
as the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
process all over again.  Initiatives to reduce time from submission to
publication have emerged across the scientific community. Rohr et al.
\cite{roh09} called for the recycling and reuse of peer-reviews:
by attaching previous reviews and detailed replies to a new submission, both
the editor and the referees can gauge the work done on the manuscript, and
perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
of Science} initiative allows authors to seek anonymous pre-review by their
peers. Some journals now accept to publish papers which received good
evaluations, with \emph{Animal Biology} having recently accepted first a paper
reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
outsourcing the review process. A widespread use of preprint servers can
achieve the same goal of reducing the time spent in review. By putting a
manuscript for open comments and criticisms, the authors will receive valuable
feedback and can improve the version which will be submitted. With a rich
enough community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread and will overall
increase the quality of first submissions.
